On Extending a Full-Sharing Design with Batched Scheduling

### 2015-04-16 paper.tex
removing stuff

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Full-Sharing with Batched Scheduling}

In this section, we show how we have extended the FS design to support
batched scheduling. The usage of batched scheduling with the FS design
requires further support since with batched scheduling, answers are
immediately propagated and we have to ensure that the propagation of
an answer occurs on all subgoal calls one and only once. To do so,
next we show a procedure that, for every subgoal call of every thread,
keeps track of all the answers that were already propagated.

@@

Figure~\ref{fig_tabtries_pcc} shows the key data structures for
supporting the implementation of the PAC procedure during the
evaluation of a tabled subgoal call $i$ using the FS design. The FS
design, uses a subgoal entry data structure to store common
information for a subgoal call and a subgoal frame (\emph{SF}) data
structure to store private information about the execution of each
thread. The PAC procedure works at the subgoal frame level, which is
private to each thread.

@@

Figure~\ref{fig_tabtries_pcc}(a) shows then a situation where two
threads, $T_1$ and $T_{k-1}$, are sharing the same subgoal entry call
$i$ when the subgoal is still under evaluation, i.e., the subgoal is
not yet complete. The current state of the evaluation shows an answer
trie with $3$ answers found for the subgoal call $i$. For the sake of
simplicity, we are omitting the internal answer trie nodes and we are
only showing the leaf nodes nodes $LN_1$, $LN_2$ and $LN_3$, in the
figure. With the PAC procedure, the leaf nodes are not chained in the
answer trie data structure. Now, the chaining process is done
privately, and for that, we use the subgoal frame structure of each
thread. On the subgoal frame structure we added a new field, called
\emph{consumer}, to store the answers found within the execution of
the thread. In order to minimize the impact of the \emph{PAC}
optimization, each node within the new consumer answer structure has
two fields: (i) an entry pointer, which points to the corresponding
leaf node in the answer trie data structure; (ii) a next pointer to
chain the answers within the consumer structure. To maintain a good
performance, when the number of nodes exceeds a certain threshold, we
use a hash trie mechanism design similar to the one presented in the
work~\cite{Areias-ijpp15}. However, since this mechanism is private to
each thread, it does not require any of the tools that were necessary
to support concurrency. In particular, on each hash trie level, we
have removed the tools necessary to support concurrency, such as
useless pointers and compare-and-swap operations. We have chosen this
hashing mechanism, because it showed a good balance between lookup and
insert operations~\cite{Areias-ijpp15}, but the major reason was
mostly because of the integration in the TabMalloc memory
allocator~\cite{Areias-12b}.

@@

Figure~\ref{fig_tabtries_pcc}(b) shows the state of the subgoal call
after completion (recall that after completion of a subgoal call, the
threads use loader nodes to consume the answers). When a thread $T$
completes a subgoal call, it frees its private consumer structures,
but before doing that, it checks whether another thread as already
marked the subgoal as completed. If no other thread has done that,
then thread $T$ not only follows its private chaining mechanism as it
would for freeing its private nodes, but also, follows the pointers to
the answer trie leaf nodes in order to reproduce the chain inside the
answer trie. Since this procedure is done inside a critical region, no
more than one thread can be doing this chaining process. Thus, in
Figure~\ref{fig_tabtries_pcc}(b), we are showing a situation where the
subgoal call is completed and both threads $T_1$ and $T_{k-1}$ have
already removed their consumer answer structures and chained the leaf
nodes inside the answer trie.

@@

At the implementation level, the major difference between local and
batched scheduling is in the tabling operation \emph{tabled new
  answer}, where we decide what to do when an answer is found during
the evaluation. This operation checks whether a newly found answer is
already in the corresponding answer trie structure and, if not,
inserts it. This requires minor changes to the \emph{tabled new
  answer} tabling
operation. Algorithm~\ref{alg_table_new_answer_batched} shows how we
have extended the tabled new answer operation to support the FS design
with batched scheduling.

@@

We now present experimental results about the usage of the batched
scheduling on the \emph{NS}, \emph{SS} and \emph{FS} designs. The
environment for our experiments was a machine with 32-Core AMD Opteron
(TM) Processor 6274 (2 sockets with 16 cores each) with 32G of main
memory, each processor with caches $L1$, $L2$ and $L3$ respectively
with the sizes of 64K, 2048K and 6144K, running the Linux kernel is
the 3.16.7-200.fc20.x86\_64, with Yap 6.3 compiled with gcc 4.8.

We used five sets of benchmarks. The \emph{Large Joins} and
\emph{WordNet} sets were obtained from the OpenRuleBench
project~\cite{Liang-09}; the \emph{Model Checking} set includes three
different specifications and transition relation graphs usually used
in model checking applications; the \emph{Path Left} and \emph{Path
  Right} sets implement two recursive definitions of the well-known
$path/2$ predicate, that computes the transitive closure in a graph,
using several different configurations of $edge/2$ facts. We
experimented graphs with the \emph{BTree} configuration with depth 17,
the \emph{Pyramid} and \emph{Cycle} configurations with depth 2000 and
the \emph{Grid} configuration with depth 35.

%% In order to have a deeper insight on the behavior of each benchmark,
%% and therefore clarify some of the results that are presented next, we
%% first characterize the benchmarks. The columns in
%% Table~\ref{tab_benchs} have the following meaning: (i) {\bf calls:} is
%% the number of different calls to tabled subgoals. It corresponds to
%% the number of paths in the subgoal tries. (ii) {\bf trie nodes:} is
%% the total number of trie nodes allocated in the corresponding
%% subgoal/answer trie structures. (iii) {\bf trie depth:} is the
%% minimum/average/maximum number of trie node levels required to
%% represent a path in the corresponding subgoal/answer trie
%% structures. Trie structures with smaller average values are more
%% amenable to higher lock contention. (iv) {\bf unique:} is the number
%% of different tabled answers found. It corresponds to the number of
%% paths in the answer tries. (v) {\bf repeated:} is the number of
%% redundant tabled answers found. (vi) {\bf NS:} is the average
%% execution time, in seconds, of ten runs for 1 thread with the NS
%% design without the TabMalloc memory allocator. In what follows, we
%% will use these times as the base times when computing the overhead
%% ratios for the other designs.

%% By observing Table~\ref{tab_benchs}, the \emph{Mondial} benchmark,
%% from the \emph{Large Joins} set, and the three \emph{Model
%%   Checking} benchmarks seem to be the benchmarks least amenable to
%% lock contention since they are the ones that find less unique answers
%% and that have the deepest trie structures. In this regard, the
%% \emph{Path Left} and \emph{Path Right} sets correspond to the
%% opposite case. They find a huge number of answers and have very
%% shallow trie structures. On the other hand, the \emph{WordNet} and
%% \emph{Path Right} sets have the benchmarks with the largest number
%% of different subgoal calls, which can reduce the probability of lock
%% contention because answers can be found for different subgoal calls
%% and therefore be inserted with minimum overlap. On the opposite side
%% are the \emph{Join2} benchmark, from the \emph{Large Joins} set,
%% and the \emph{Path Left} benchmarks, which have only a single tabled
%% subgoal call.

%% \begin{table}[ht]
%% \centering
%% \caption{Characteristics of the benchmark programs}
%% \scalebox{0.82} { 
%% \begin{tabular}{lrrccrrrcc}
%% \hline\hline
%% \multirow{2}{*}{\bf Bench}
%% & \multicolumn{3}{c}{\bf Tabled Subgoals}
%% &
%% & \multicolumn{4}{c}{\bf Tabled Answers}
%% & \multicolumn{1}{c}{\bf Time (sec)} \\ \cline{2-4}\cline{6-9}
%% & \multicolumn{1}{c}{\bf calls}
%% & \multicolumn{1}{c}{\bf trie nodes}
%% & \multicolumn{1}{c}{\bf trie depth}
%% &
%% & \multicolumn{1}{c}{\bf unique}
%% & \multicolumn{1}{c}{\bf repeated}
%% & \multicolumn{1}{c}{\bf trie nodes}
%% & \multicolumn{1}{c}{\bf trie depth}
%% & \multicolumn{1}{c}{\bf NS} \\
%% \hline
%% \multicolumn{10}{l}{\bf Large Joins} \\
%% \bf{Join2}    &       1 &       6 & 5/5/5 && 2,476,099 &         0 &
%% 2,613,660 &    5/5/5 &  2.85 \\
%% \bf{Mondial}  &      35 &      42 & 3/4/4 &&     2,664 & 2,452,890 &
%%    14,334 &    6/7/7 &  0.84 \\
%% \hline
%% \multicolumn{10}{l}{\bf WordNet} \\
%% \bf{Clusters} & 117,659 & 235,319 & 2/2/2 &&   166,877 &   161,853 &
%% 284,536 &    1/1/1 &   0.83 \\
%% \bf{Holo}     & 117,657 & 235,315 & 2/2/2 &&    74,838 &        54 &
%% 192,495 &    1/1/1 &   0.75 \\
%% \bf{Hyper}    & 117,657 & 235,315 & 2/2/2 &&   698,472 &     8,658 &
%% 816,129 &    1/1/1 &   1.42 \\
%% \bf{Hypo}     & 117,657 & 117,659 & 2/2/2 &&   698,472 &    20,341 &
%% 816,129 &    1/1/1 &   1.53 \\
%% \bf{Mero}     & 117,657 & 117,659 & 2/2/2 &&    74,838 &        13 &
%% 192,495 &    1/1/1 &   0.74 \\
%% \bf{Tropo}    & 117,657 & 235,315 & 2/2/2 &&       472 &         0 &
%% 118,129 &    1/1/1 &   0.66 \\
%% \hline
%% \multicolumn{10}{l}{\bf Model Checking} \\
%% \bf{IProto}   &       1 &       6 & 5/5/5 &&   134,361 &   385,423 &
%% 1,554,896 &  4/51/67 & 2.70 \\
%% \bf{Leader}   &       1 &       5 & 4/4/4 &&     1,728 &   574,786 &
%%    41,788 & 15/80/97 & 3.51  \\
%% \bf{Sieve}    &       1 &       7 & 6/6/6 &&       380 & 1,386,181 &
%%     8,624 & 21/53/58 & 18.50 \\
%% \hline
%% \multicolumn{10}{l}{\bf Path Left} \\
%% \bf{BTree}    &       1 &       3 & 2/2/2 && 1,966,082 &         0 &
%% 2,031,618 &    2/2/2 &   1.53 \\
%% \bf{Cycle}    &       1 &       3 & 2/2/2 && 4,000,000 &     2,000 &
%% 4,002,001 &    2/2/2 &   3.52 \\
%% \bf{Grid}     &       1 &       3 & 2/2/2 && 1,500,625 & 4,335,135 &
%% 1,501,851 &    2/2/2 &  1.93 \\
%% \bf{Pyramid}  &       1 &       3 & 2/2/2 && 3,374,250 & 1,124,250 &
%% 3,377,250 &    2/2/2 &   3.08 \\
%% \hline
%% \multicolumn{10}{l}{\bf Path Right} \\
%% \bf{BTree}    & 131,071 & 262,143 & 2/2/2 && 3,801,094 &         0 &
%% 3,997,700 &    1/2/2 &  2.33 \\
%% \bf{Cycle}    &   2,001 &   4,003 & 2/2/2 && 8,000,000 &     4,000 &
%% 8,004,001 &    1/2/2 &  3.55 \\
%% \bf{Grid}     &   1,226 &   2,453 & 2/2/2 && 3,001,250 & 8,670,270 &
%% 3,003,701 &    1/2/2 &  2.32 \\
%% \bf{Pyramid}  &   3,000 &   6,001 & 2/2/2 && 6,745,501 & 2,247,001 &
%% 6,751,500 &    1/2/2 &  3.17 \\
%% \hline\hline
%% \end{tabular}}
%% \label{tab_benchs}
%% \end{table}

%% Note that for the moment our goal is to evaluate the robustness of our
%% implementation when exposed to \emph{worst case} scenarios. By
%% focusing on \emph{worst case} scenarios, we show the lowest bounds in
%% terms of performance that each design might achieve when applied/used
%% with other real world applications/programs. Moreover, by testing the
%% framework with worst case scenarios, we avoid the peculiarities of the
%% program at hand and we try to focus on measuring the real value of our
%% designs. Thus, we will follow a common approach to create worst case
%% scenarios and we will run all threads starting with the same query
%% goal. By doing this, it is expected that all threads will access the
%% table space, to check/insert for subgoals and answers, at similar
%% times, thus causing a huge stress on the same critical regions. To put
%% the results in perspective, we experimented with $1$, $8$, $16$, $24$
%% and $32$ threads (the maximum number of cores available in our
%% machine) with local and batched scheduling on the five sets of
%% benchmarks presented in the early subsection.

Table~\ref{tab_batched_overhead} shows the overhead ratios, when
compared with the NS design with 1 thread (running with local
scheduling), for the NS and FS designs (all running TabMalloc), when
running 1, 8, 16, 24 and 32 threads with local and batched scheduling
on the five sets of benchmarks. For each design, the table has then
two columns, a column with {\bf Local} that shows results for the
local scheduling and a column with {\bf Batched} with results for
batched scheduling. The overhead results presented in both {\bf Local}
and {\bf Batched} columns use as base time the execution times
presented in the {\bf NS} column of the Table~\ref{tab_benchs}.

\setlength{\tabcolsep}{12pt}

\begin{table}[!ht]
\vspace{-\intextsep}
\centering
\caption{Overhead ratios, when compared with the NS design with $1$
  thread (running with local scheduling without TabMalloc) for the NS
  and FS designs (with TabMalloc), when running 1, 8, 16, 24 and 32
  threads with local and batched scheduling on the five sets of
  benchmarks (best ratios by row and by design for the Minimum,
  Average and Maximum are in bold)}
\vspace{-0.5\intextsep}
%\scalebox{1.00} {
\begin{tabular}{ll|cc|cc}
\hline\hline
\multicolumn{2}{c|}{\multirow{2}{*}{\bf Threads}} &
\multicolumn{2}{c|}{\multirow{1}{*}{\bf NS}} &
\multicolumn{2}{|c}{\multirow{1}{*}{\bf FS}}\\ \cline{3-6}
& 
& \multicolumn{1}{c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}
& \multicolumn{1}{|c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}\\
\hline
\multirow{4}{*}{\bf 1}
& {\bf Min }& {\bf 0.53}& 0.55& 1.01& {\bf 0.95}\\
& {\bf Avg }& {\bf 0.78}& 0.82& {\bf 1.30}& 1.46\\
& {\bf Max }& 1.06& {\bf 1.05}& {\bf 1.76}& 2.33\\
& {\bf StD }& 0.15& 0.14& 0.22& 0.44\\
\hline
\multirow{4}{*}{\bf 8}
& {\bf Min }& 0.66& {\bf 0.63}& 1.16&{\bf  0.99}\\
& {\bf Avg }& {\bf 0.85}& 0.88& {\bf 1.88}& 1.95\\
& {\bf Max }& {\bf 1.12}& 1.14& {\bf 2.82}& 3.49\\
& {\bf StD }& 0.13& 0.14& 0.60& 0.79\\
\hline
\multirow{4}{*}{\bf 16}
& {\bf Min }& 0.85& {\bf 0.75}& 1.17& {\bf 1.06}\\
& {\bf Avg }& {\bf 0.98}& 1.00& {\bf 1.97}& 2.08\\
& {\bf Max }& {\bf 1.16}& 1.31& {\bf 3.14}& 3.69\\
& {\bf StD }& 0.09& 0.17& 0.65& 0.83\\
\hline
\multirow{4}{*}{\bf 24}
& {\bf Min }& {\bf 0.91}& 0.93& 1.16& {\bf 1.09}\\
& {\bf Avg }& {\bf 1.15}& 1.16& {\bf 2.06}& 2.19\\
& {\bf Max }& 1.72& {\bf 1.60}& {\bf 3.49}& 4.08\\
& {\bf StD }& 0.20& 0.21& 0.70& 0.91\\
\hline
\multirow{4}{*}{\bf 32}
& {\bf Min }& 1.05& {\bf 1.04}& 1.33& {\bf 1.26}\\
& {\bf Avg }& 1.51& {\bf 1.49}& {\bf 2.24}& 2.41\\
& {\bf Max }& {\bf 2.52}& 2.63& {\bf 3.71}& 4.51\\
& {\bf StD }& 0.45& 0.45& 0.74& 1.02\\
\hline\hline
\end{tabular}%}
\label{tab_batched_overhead}
\vspace{-0.7\intextsep}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Extending Full-Sharing with Batched Scheduling}

In this section, we show how we have extended the FS design to support
batched scheduling. The usage of FS design with batched scheduling,
requires further support than with local scheduling, since when a new
answer is found it must be immediately propagated, and we have to
ensure that the propagation occurs on all subgoal calls once and only
once. To do so, next we show a procedure that, for every subgoal call
of every thread, keeps track of all the answers that were already
propagated.

@@

Figure~\ref{fig_tabtries_pcc} shows the key data structures for
supporting the implementation of the PAC procedure during the
evaluation of a tabled subgoal call $i$ using the FS design. %% The FS
%% design, uses a subgoal entry data structure to store common
%% information for a subgoal call and a subgoal frame (\emph{SF}) data
%% structure to store private information about the execution of each
%% thread.
The PAC procedure works at the subgoal frame level, which is
private to each thread.

@@

Figure~\ref{fig_tabtries_pcc}(a) shows then a situation where two
threads, $T_1$ and $T_{k-1}$, are sharing the same subgoal entry call
$i$ when the subgoal is still under evaluation, i.e., the subgoal is
not yet complete. The current state of the evaluation shows an answer
trie with $3$ answers found for the subgoal call $i$. For the sake of
simplicity, we are omitting the internal answer trie nodes and we are
only showing the leaf nodes nodes $LN_1$, $LN_2$ and $LN_3$, in the
figure. %% With the PAC procedure, the leaf nodes are not chained in the
%% answer trie data structure. Now, the chaining process is done
%% privately, and for that, we use the subgoal frame structure of each
%% thread.
On the subgoal frame structure we added a new field, called
\emph{consumer}, to store the answers found within the execution of
the thread. In order to minimize the impact of the \emph{PAC}
optimization, each node within the new consumer answer structure has
two fields: (i) an entry pointer, which points to the corresponding
leaf node in the answer trie data structure; (ii) a next pointer to
chain the answers within the consumer structure. To maintain a good
performance, when the number of nodes exceeds a certain threshold, we
use a hash trie mechanism design similar to the one presented in the
work~\cite{Areias-ijpp15}. However, since this mechanism is private to
each thread, it does not require any of the tools that were necessary
to support concurrency, thus we have removed them from the mechanism.

%% In particular, on each hash trie level, we
%% have removed the tools necessary to support concurrency, such as
%% useless pointers and compare-and-swap operations. We have chosen this
%% hashing mechanism, because it showed a good balance between lookup and
%% insert operations~\cite{Areias-ijpp15}, but the major reason was
%% mostly because of the integration in the TabMalloc memory
%% allocator~\cite{Areias-12b}.

@@

Figure~\ref{fig_tabtries_pcc}(b) shows the state of the subgoal call
after completion. When a thread $T$ completes a subgoal call, it frees
its private consumer structures, but before doing that, it checks
whether another thread as already marked the subgoal as completed. If
no other thread has done that, then thread $T$ not only follows its
private chaining mechanism as it would for freeing its private nodes,
but also, follows the pointers to the answer trie leaf nodes in order
to create a chain inside the answer trie. Since this procedure is done
inside a critical region, no more than one thread can be doing this
chaining process. Thus, in Figure~\ref{fig_tabtries_pcc}(b), we are
showing a situation where the subgoal call is completed and both
threads $T_1$ and $T_{k-1}$ have already removed their consumer answer
structures and chained the leaf nodes inside the answer trie.

@@

At the tabling engine, the major difference between local and batched
scheduling is in the tabling operation \emph{tabled new answer}, where
we decide what to do when an answer is found during the
evaluation. This operation checks whether a newly found answer is
already in the corresponding answer trie structure and, if not,
inserts it. Algorithm~\ref{alg_table_new_answer_batched} shows how we
have extended this operation to support FS design with batched
scheduling.

@@

We now present experimental results about the usage of the batched
scheduling on FS design. To put results in perspective, we will be
showing also the results for the NS design. The environment for our
experiments was a machine with 32-Core AMD Opteron (TM) Processor 6274
(2 sockets with 16 cores each) with 32G of main memory, running the
Linux kernel is the 3.16.7-200.fc20.x86\_64 with Yap 6.3.

For the experimentation, we used our memory allocator described in the
work~\cite{Areias-12b}, later named \emph{TabMalloc}, and we the same
five sets of benchmarks. These benchmarks create \emph{worst case}
scenarios, where we are able to show the lowest bounds in terms of
performance that each design might achieve when applied/used with
other real world applications/programs.

Table~\ref{tab_batched_overhead} shows the overhead ratios, when
compared with the NS design with 1 thread (running with local
scheduling without TabMalloc), for the NS and FS designs, when running
1, 8, 16, 24 and 32 threads, with TabMalloc and, local scheduling
(column \emph{Local}) and batched scheduling (column \emph{Batched})
strategies. In order to give a fair weight to each benchmark, the
overhead ratio is calculated as follows. We begin by running ten times
each benchmark $B$ for each design $D$ with $T$ threads. Then, we
calculate the average of those ten runs and use that value ($D_{BT}$)
to put it in perspective against the base time, which is the average
of the ten runs of the NS design with $1$ thread ($NS_{B1}$). For
that, we use the following formula for the overhead $O_{DBT} = D_{BT}
/ NS_{B1}$.  After calculating all the overheads $O_{DBT}$ for a
certain design $D$ and number of threads $T$ corresponding to the
several benchmarks $B$, we calculate the respective minimum, average,
maximum and standard deviation overhead ratios. Thus, the lowest ratio
is the one that represents lowest overhead and it is the best ratio.

\setlength{\tabcolsep}{12pt}
\begin{table}[!ht]
\vspace{-\intextsep}
\centering
%% \caption{Overhead ratios, when compared with the NS design with $1$
%%   thread (running with local scheduling without TabMalloc) for the NS
%%   and FS designs (with TabMalloc), when running 1, 8, 16, 24 and 32
%%   threads with local and batched scheduling on the five sets of
%%   benchmarks (best ratios by row and by design for the Minimum,
%%   Average and Maximum are in bold)}
\caption{Overhead ratios, when compared with the NS design with 1
  thread for the NS and FS designs, when running 1, 8, 16, 24 and 32
  threads with local and batched scheduling (lowest is the best and it
  is marked in bold by row and by design for the Minimum, Average and
  Maximum)}
\vspace{-0.5\intextsep}
%\scalebox{1.00} {
\begin{tabular}{ll|cc|cc}
\hline\hline
\multicolumn{2}{c|}{\multirow{2}{*}{\bf Threads}} &
\multicolumn{2}{c|}{\multirow{1}{*}{\bf NS}} &
\multicolumn{2}{|c}{\multirow{1}{*}{\bf FS}}\\ \cline{3-6}
& 
& \multicolumn{1}{c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}
& \multicolumn{1}{|c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}\\
\hline
\multirow{4}{*}{\bf 1}
& {\bf Min }& {\bf 0.53}& 0.55& 1.01& {\bf 0.95}\\
& {\bf Avg }& {\bf 0.78}& 0.82& {\bf 1.30}& 1.46\\
& {\bf Max }& 1.06& {\bf 1.05}& {\bf 1.76}& 2.33\\
& {\bf StD }& 0.15& 0.14& 0.22& 0.44\\
\hline
\multirow{4}{*}{\bf 8}
& {\bf Min }& 0.66& {\bf 0.63}& 1.16&{\bf  0.99}\\
& {\bf Avg }& {\bf 0.85}& 0.88& {\bf 1.88}& 1.95\\
& {\bf Max }& {\bf 1.12}& 1.14& {\bf 2.82}& 3.49\\
& {\bf StD }& 0.13& 0.14& 0.60& 0.79\\
\hline
\multirow{4}{*}{\bf 16}
& {\bf Min }& 0.85& {\bf 0.75}& 1.17& {\bf 1.06}\\
& {\bf Avg }& {\bf 0.98}& 1.00& {\bf 1.97}& 2.08\\
& {\bf Max }& {\bf 1.16}& 1.31& {\bf 3.14}& 3.69\\
& {\bf StD }& 0.09& 0.17& 0.65& 0.83\\
\hline
\multirow{4}{*}{\bf 24}
& {\bf Min }& {\bf 0.91}& 0.93& 1.16& {\bf 1.09}\\
& {\bf Avg }& {\bf 1.15}& 1.16& {\bf 2.06}& 2.19\\
& {\bf Max }& 1.72& {\bf 1.60}& {\bf 3.49}& 4.08\\
& {\bf StD }& 0.20& 0.21& 0.70& 0.91\\
\hline
\multirow{4}{*}{\bf 32}
& {\bf Min }& 1.05& {\bf 1.04}& 1.33& {\bf 1.26}\\
& {\bf Avg }& 1.51& {\bf 1.49}& {\bf 2.24}& 2.41\\
& {\bf Max }& {\bf 2.52}& 2.63& {\bf 3.71}& 4.51\\
& {\bf StD }& 0.45& 0.45& 0.74& 1.02\\
\hline\hline
\end{tabular}%}
\label{tab_batched_overhead}
\vspace{-0.7\intextsep}
\end{table}
